\textbf{Optimization of Porous Silicon Gradient Refractive Index Structures.}

### 2020-06-17 paper.tex
Revise up to conclusions

\subsection{PS GRIN Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MicrGrin}
  \caption{\notaL{Está bonita la figura, pero tiene errores. La
      superficie del electrolito y la superficie de la muestra
      deben ser ambas horizontales. Cambia la fuente por fuente
      de corriente. La punta del electrodo no debe ser una
      bola. Quita todo lo que está abajo del sustrato. Mejor pon
      solamente una H en alguna región amarilla y una L en
      alguna región azul. El electrolito tiene gotas o
      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
      anchos totales, pues no creo que nos sean útiles. Haz que los cables
      horizontales sean horizontales.}
    PS GRIN microcavity made of layers of high (H) and low (L)
    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
    arranged in the sequence $(HL)_NHH(HL)_N$. Both the index of
    refraction and the widths depend on position along the
    sample and are chosen to obey a quarter wavelength
    condition at a given position $A$ and wavelength $\lambda_c$.
  }
  \label{fig:MCGRIN0}
\end{figure}

@@

\begin{table}
  \begin{tabular}{ccccccc}
    \hline
    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
    \hline
    \hline
    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
    A(L) & 44  & 0.74& 1.44& 0.65   \\
    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
    B(L) & 32  & 0.68& 2.29& 0.58   \\
    C(H) & 3.0 & 0.39& 2.81&0.54    \\
    C(L) & 24  & 0.64& 2.30&0.54    \\
  \end{tabular}
  \caption{Some properties of the PS GRIN MC corresponding to the
    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
    low ($L$) index layers. The current densities were obtained by
    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
    $I_L$, the depths were obtained from the etching
    times and the current density using \eqref{eq:etch}, the porosity
    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
    the resonant wavelengths of the cavity were read from
    Fig. \ref{fig:MCGRIN3}.
    \notaL{Inventé lo de arriba. Qué es cierto y qué
      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
      0.67 en A?} \notaL{¿De dónde sacaste
        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
        ¿no? quité los tiempos pues son los mismos. Quité las
        posiciones pues están descritas antes. Añade una columna
        con las profundidades $d_H$ y $d_L$. }}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
sample, which displays a color that shifts towards the blue when we
move towards its right, that is, away from where the electrode was
positioned. In the figure we indicate three points with $x$ coordinate
$x_A=0.3\text{cm)$ , $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$.
  \notaL{***Aquí voy***}
  Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_H=35 s $, with a high refractive index $n_H \sim$ $
2,661$ to $ 2,808$ and porosities of $P_H \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_H=11 s$  for low refractive index
$n_L\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_H \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_i =
       (N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}
	\label{fig:MCGRIN4}

For the Fig. \ref{fig:MCGRIN4} shows the SEM cross-sectional images of
the PS samples used in this work. Relatively small interface
roughness and a clear contrast between the high and low porosity of
the microcavity measured at different points (A, B and C), showing the
change in thickness in each of these. The measured thicknesses of the
complete multi-film structures showed good agreement with the
simulations taken from $ V = 0.53J^{0.79} $ where $d_j=Vt_j$
($j=H,L$), which are the thicknesses of each of the monolayer of the
porous silicon microcavity GRIN at the measurement points and the
total thickness we find it as $d_i =
(N_{Hi}d_{Hi})+(N_{Li}d_{Li}) + (2d_{Hi})$ defining $ i
= $ A, B, C. Which resulted in (measured / simulation) $ 2.25 / 2.31 \
\ \mu m $ (for structure at Point A), $ 2.17 / 2.08 \ \ \mu m $ (for
structure at point B) and $ 1.87 / 1.65 \ \ \mu m $ (for structure at
point C).
Being able to say that for each measurement point corresponds
different calculated current densities, which correspond to different
thicknesses at the end of manufacturing, clearly seeing the lateral
gradient product of our experiment.

\section{conclusion}
\label{sec:conclusion}
The necessary expressions for the potential components were derived,
finding a relationship of the tip of the counter electrode that acts
similarly as a point charge and the current density for a geometry in
a rectangular electrolytic box and we solve the electrostatic
equations with suitable boundary conditions. Resulting in an
electrostatic model for  Photonics crystals with a refractive index
with gradient (EMPCGRIN).
It is the first time that the formalism mentioned here has been
applied to find the current density to design porous silicon. The
shape of the electrode, the area of the cell produces a visible
decrease in the size and density of the pores. Additionally,
optimizing the structural properties for a single structure we could
have a gradient with different depths, reflactances at differents
measurement points. In this way, we were able to simulate the direct
relationship of the attack speed with the current density at the
points  the samples of interest. At the same time, we developed a
characterization between porosity, refractive indices of porous
silicon, with the different current densities. And in the end we were
able to design and characterize Porous Silicon microcavities with
refractive indices with gradients, which for each measurement point
correspond to different calculated current densities, which correspond
to different thicknesses, clearly seeing the lateral gradient product
of our experiment.
\section{Acknowledgments}
\label{sec:acknowledgments}
% \backmatter
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
\bibliographystyle{unsrt}
\begin{thebibliography}{X}
  % forma de biblio es MLA
\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
  Publication,
  USA, 2005).
\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
  Malvern, UK.
\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
      Theoretical Study of the Formation and Microstructure of
      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
    622?36. doi:10.1021/jp0706984. }
\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
    Quantum Wire Array Fabrication by Electrochemical and Chemical
    Dissolution of Wafers.\textquotedblright} Applied Physics
  Letters 57 (10): 1046. doi:10.1063/1.103561.
\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
  \emph{Photonic Crystals: Molding the Flow of
    Light}\textquotedblright, 2nd edn.
  (Princeton University Press, UK, 2008).
\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
  283-295 (1993)
\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
    Optical devices from porous silicon having continuously varying
    refractive index.}\textquotedblright Journal of Materials
  Science: Materials in Electronics 18.1 (2007): 61-64.
\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
    a nonlinear photonic crystal: a numerical
    study.}\textquotedblright Optics letters 21.15 (1996):
  1138-1140.
\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
  V. Agarwal. \textquotedblleft \emph{White metal-like
    omnidirectional mirror from porous silicon dielectric
    multilayers.}\textquotedblright Applied Physics Letters 101.3
  (2012): 031119.
\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
  \emph{Linear waveguides in photonic-crystal
    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.

>>>>

\subsection{PS GRIN Microcavities}
\label{sec:grin-porous-silicon}
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Images/MicrGrin}
  \caption{\notaL{Está bonita la figura, pero tiene errores. La
      superficie del electrolito y la superficie de la muestra
      deben ser ambas horizontales. Cambia la fuente por fuente
      de corriente. La punta del electrodo no debe ser una
      bola. Quita todo lo que está abajo del sustrato. Mejor pon
      solamente una H en alguna región amarilla y una L en
      alguna región azul. El electrolito tiene gotas o
      burbujas. Tal vez sea mejor ponerle un color uniforme. Quita los
      anchos totales, pues no creo que nos sean útiles. Haz que los cables
      horizontales sean horizontales.}
    PS GRIN microcavity made of layers of high (H) and low (L)
    refractive index $n_H$ and $n_L$ and widths $d_H$ and $d_L$
    arranged in the sequence $(HL)_NHH(HL)_N$. \notaL{CUánto vale $N$?
    Antes habías dicho que 6, pero en la figura 12 parece otra cosa} Both the index of
    refraction and the widths depend on position along the
    sample and are chosen to obey a quarter wavelength
    condition at a given position $A$ and wavelength $\lambda_c$.
  }
  \label{fig:MCGRIN0}
\end{figure}

@@

\begin{table}
  \centering
  \begin{tabular}{ccccccc}
    \hline
    Pos(kind)&Current(mA/cm$^2$)&Porosity&Index&Wavelength($\mu\text{m}$)\\
    \hline
    \hline
    A(H) & 5.5 & 0.45& 2.66& 0.65   \\
    A(L) & 44  & 0.74& 1.44& 0.65   \\
    B(H) & 4.0 & 0.41& 2.76& 0.58   \\
    B(L) & 32  & 0.68& 2.29& 0.58   \\
    C(H) & 3.0 & 0.39& 2.81&0.54    \\
    C(L) & 24  & 0.64& 2.30&0.54    \\
  \end{tabular}
  \caption{Some properties of the PS GRIN MC corresponding to the
    positions $A$, $B$ and $C$ and the corresponding high ($H$) and
    low ($L$) index layers. The current densities were obtained by
    scaling the results in Fig. \ref{fig:DR1} with $I_H$ and
    $I_L$, the depths were obtained from the etching
    times and the current density using \eqref{eq:etch}, the porosity
    was obtained from Eq. \eqref{eq:poros}, the indices of refraction
    were obtained from Eq. \eqref{Eq:Brugg} using the porosity, and
    the resonant wavelengths of the cavity were read from
    Fig. \ref{fig:MCGRIN3}.
    \notaL{Inventé lo de arriba. Qué es cierto y qué
      mentira?}\notaL{Por qué resuenas en 0.65 si habías diseñado
      0.67 en A?} \notaL{¿De dónde sacaste
        $\lambda_c$ para los otros puntos? ¿Cómo le hiciste para que
        $\lambda_c$ diera lo mismo en $H$ y en $L$? $n$ y $k$ dependen de la
        frecuencia. ¿Qué frecuencia usaste para darles valores en esta
        tabla?}\notaL{quité digitos a n. quité k pues es chiquita,
        ¿no? quité los tiempos pues son los mismos. Quité las
        posiciones pues están descritas antes. Añade una columna
        con las profundidades $d_H$ y $d_L$. }\notaL{De los rótulos de
      la figura quita las palabras Point. Cambia simulation por Theory.}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} we show a photograph of a PS GRIN MC
sample, which displays a color that shifts towards the blue when we
move towards its right, that is, away from where the electrode was
positioned. In the figure we indicate three points with $x$ coordinates
$x_A=0.3\text{cm}$,  $x_B=0.8\text{cm}$, and $x_C=1.2\text{cm}$
on we measured the reflectance spectra, also shown in the figure.
\notaL{No dices cómo hiciste las curvas teóricas} The spectra have the
expected shape: a high reflectance plateau corresponding to the
photonic band gap of the Bragg mirror, with a deep narrow minimum due
to the Fabry-Perot resonance of the cavity. We also present the
calculated spectra. To that end, we calculated the current density
using the theory developed in Sec. \ref{sec:calc-curr-dens}, i.e., by
scaling Fig. \ref{fig:DR1} with the total current $I_H$ and $I_L$ used
to fabricate each layer. From the current densities we obtained the
corresponding etching rates and the porosities using
Eqs.~\eqref{eq:etch} and  \eqref{eq:poros}, and from the, the
thickness of each layer, the index of refraction
(Eq. \eqref{Eq:Brugg}) and the reflectance,using standard transfer
matrix theory \notaL{ref}. Notice the good agreement between theory
and experiment. \notaL{No me lo creo. Me sospecho que más bien,
  ajustaste el experimento no sé con qué parámetro. Explícame cómo
  hiciste el cálculo.} The parameters used are shown in Table \ref{tabla:1}.
\notaL{No entiendo qué quisiste decir aquí: For theoretical values, we
  use complex refractive indices as free parameters to fit the
  experimental refractive spectra (Section 4.2).} The band-gap, the
resonance and the oscillations due to multiple reflections in the
region of transparency are similar, though the experimental spectra is
more rounded and the central resonance is wider. This might be due to
the roughness of the interfaces, which would lead to some scattering
whose effects are similar to those of an additional absorption
\ref{cita el artículo en prensa de Guille y mío}.\notaL{Checar que no
  diga mentiras arriba. El ajuste es demasiado bueno, pero no sé cómo
  se hizo. Hay que explicar qué significan y de dónde salieron las
  $\lambda_c$ de la tabla. }

 \begin{figure}
   \centering
   \includegraphics[width=\textwidth]{Images/MCGRINSEM}
   \caption{Cross section SEM images corresponding to the positions
     $A$, $B$, and $C$ of the PS GRIN MC shown in
     Fig. \ref{fig:MCGRIN3}. The total thickness of the system at
     different positions, $d_A=2.25\mu\text{m}$,
     $d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ are
     indicated. \notaL{Porque se ve una capa más ancha a la izquierda?
       ¿Por qué el número de capas arriba no es igual que abajo? ¿Por
       qué el número de capas no es el mismo en las distintas fotos?
       ¿Por qué no es 6 como dice el texto en la
       Sec. \ref{sec:fabrication-grin-ps}?}
     }
   \label{fig:MCGRIN4}
 \end{figure}
In Fig. \ref{fig:MCGRIN4} we show SEM cross-sectional images of
the PS GRIN MC sample. We can appreciate a relatively small interface
roughness and a clear contrast between the high and low porosity
layers. The structure of the microcavity is also visible, with a
central layer of twice the thickness of the corresponding layers
within the Bragg mirrors. The gradient of the thickness is also
evident, as $d_A>d_B>d_C$, with $d_A=2.25\mu\text{m}$,
$d_B=2.17\mu\text{m}$, and $d_C=1.87\mu\text{m}$ the total thickness
of the structure measured at the positions $A$, $B$, and $C$.
The measured thickness are in good agreement with those computed from
the current densities and the etching times $N(d_H+d_L)+2 d_H$ using
Eq. \eqref{eq:etch}, where $N$ is the number of pairs of layers in the
Bragg mirrors, which yield $d_A=2.31\mu\text{m}$,
$d_B=2.08\mu\text{m}$, and $d_C=1.65\mu\text{m}$. \notaL{Por qué una
  te dio más grande y las otras más chicas? Aquí tienes que decir
  cuánto vale $N$ y no has dicho cuánto valieron $d_L$ y $d_H$}

\section{Conclusions}
\label{sec:conclusion}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive a simplel expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in reciprocal space, and it is made up of
a rapidly converging sum of analytical terms. This allowed us to
characterize the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical experiments on just a
few samples. We illustrated the procedure with two samples each of which we
measured at three different positions. These calibration curves are
very useful as the etching rate for the formation of porous silicon
and the resulting porosity is very sensitive to the growth conditions
and to the properties of the substrate, such as its doping. Thus,
there are no universal calibration curves. Having obtained these calibration curves
and being able to compute the current density at different positions
allows the prediction of the properties of GRIN structures. We
illustrated this by desigining a PS GRIN microcavity tuned at one
position to a given wavelength. We found a good agreement between its
measured reflectance spectra at different points with the spectra
calculated from the values of the expected local current
density using the calibration curves. We also found good agreement
between the measured and the expected geometry of the system. These
results show that the use of a simple electrolytic cell and our
computational procedure does allow the accurate prediction of the
optical properties of GRIN structures, and thus we believe it will
prove helpful for the design fabrication and characterization of novel
devices based on PS GRIN systems.

\section*{Acknowledgments}
\label{sec:acknowledgments}
WLM acknowledges the support of DGAPA-UNAM under grant IN111119.
% \backmatter
%\nocite{*}
%\bibliographystyle{plain}
%\bibliography{bibliografía.bib} %Aquí ponen el nombre del archivo .bib
\notaL{Manda toda la bibliografía a un archivo .bib}
\notaL{Cuando esté listo, quiero que me expliques por qué incluiste
  cada uno de los artículos citados}
\bibliographystyle{unsrt}
\begin{thebibliography}{X}
  % forma de biblio es MLA
\bibitem{I1} P. Yeh,\textquotedblleft \emph{Optical Waves in Layered
    Media} \textquotedblright, 2nd edn. (Wiley-Interscience
  Publication,
  USA, 2005).
\bibitem{I2}Canham, L. 1997.\textquotedblleft \emph{Properties of
    Porous Silicon} \textquotedblright. Edited by Canham L. DERA,
  Malvern, UK.
\bibitem{I3}{Beale, M.I.J, J.D Benjamin, M.J Uren, N.G Chew, and A.G
    Cullis. 1985. \emph{ \textquotedblleft An Experimental and
      Theoretical Study of the Formation and Microstructure of
      Porous Silicon.\textquotedblright} J. Crystal Growth 73:
    622?36. doi:10.1021/jp0706984. }
\bibitem{I4}Canham, L. T. 1990. \emph{\textquotedblleft Silicon
    Quantum Wire Array Fabrication by Electrochemical and Chemical
    Dissolution of Wafers.\textquotedblright} Applied Physics
  Letters 57 (10): 1046. doi:10.1063/1.103561.
\bibitem{I5} J. D. Joannopoulos et al.,\textquotedblleft
  \emph{Photonic Crystals: Molding the Flow of
    Light}\textquotedblright, 2nd edn.
  (Princeton University Press, UK, 2008).
\bibitem{I6} E. Yablonovitch, \textquotedblleft \emph{Photonic
    band-gap structures,}\textquotedblright J. Opt. Soc. Am. B 10,
  283-295 (1993)
\bibitem{I7} Ilyas, S., and M. Gal.  \textquotedblleft \emph{
    Optical devices from porous silicon having continuously varying
    refractive index.}\textquotedblright Journal of Materials
  Science: Materials in Electronics 18.1 (2007): 61-64.
\bibitem{I8} Tran, P. \textquotedblleft \emph{Optical switching with
    a nonlinear photonic crystal: a numerical
    study.}\textquotedblright Optics letters 21.15 (1996):
  1138-1140.
\bibitem{I9} Ariza-Flores, A. David, L. M. Gaggero-Sager, and
  V. Agarwal. \textquotedblleft \emph{White metal-like
    omnidirectional mirror from porous silicon dielectric
    multilayers.}\textquotedblright Applied Physics Letters 101.3
  (2012): 031119.
\bibitem{I10} Johnson, Steven G., et al.  \textquotedblleft
  \emph{Linear waveguides in photonic-crystal
    slabs.}\textquotedblright Physical Review B 62.12 (2000): 8212.
